% LaTeX source for "OpenStack Beginner's Guide"
% Copyright (c)  2014  pinlabs.in.

% Permission is granted to copy, distribute and/or modify this document under
% the terms of the GNU Free Documentation License, Version 1.1  or any later
% version published by the Free Software Foundation; with the Invariant
% Sections being "Contributor List", "Forward", and "Preface", with no
% Front-Cover Texts, and with no Back-Cover Texts. A copy of the license is
% included in the section entitled "GNU Free Documentation License".

% This distribution includes a file named fdl.tex that contains the text of the
% GNU Free Documentation License.  If it is missing, you can obtain it from
% www.gnu.org or by writing to the Free Software Foundation, Inc.,
% 59 Temple Place - Suite 330, Boston, MA 02111-1307, USA.
%
\chapter{Preface} 

\section*{About this guide}
The idea of OpenStack Beginner's Guide came from OpenStack cactus release, during that time we had limited documentation available. Our initial contributors were Murthyraju Manthena, Kiran Murari, Suseendran RB, Yogesh G, Atul Jha and Johnson D. We released this book updating every version and adding newer components. Later on this book got merged with official OpenStack documentaion. We thought we still need to maintain this book for our reference and hence we are releasing the book for Icehouse version on Ubuntu 14.04 LTS.

\section*{Target Audience}
Our aim has been to provide a guide for a beginners who are new to OpenStack. Good familiarity with virtualization is assumed, as troubleshooting OpenStack related problems requires a good knowledge of virtualization. Similarly, familiarity with Cloud Computing concepts and terminology will be of help. Prior exposure to AWS API and/or tools is not mandatory, though such exposure will accelerate the learning process greatly.

\section*{Acknowledgement}
Most of the content has been borrowed from web resources like manuals, documentation, white papers etc. from OpenStack and Canonical; numerous posts on forums and discussions on OpenStack IRC Channel. We would like to thank all the authors of these resources.

\section*{License}
Attribution-ShareAlike 4.0 International. For the full version of the license text, please refer to
\url{http://creativecommons.org/licenses/by-sa/4.0/legalcode} and
\url{http://creativecommons.org/licenses/by-sa/4.0/} for a shorter description.

\section*{Feedback}
We would really appreciate your feedback. We will enhance the book on an ongoing basis based on your feedback. Please mail your feedback to 
\href{mailto:books@pinlabs.in}{books@pinlabs.in}.

\vspace{0.25in}
%\begin{flushright}
%Pinlabs.in Team\\
%pinlabs.in\\
%\end{flushright}
